Analysis of bulk void regions

### 2014-06-05 cosmic_voids.tex
Updating pdf

%.........................................................................
%FIGURE 1: FA and vissual impression
\begin{flushleft}
\begin{figure*}
\centering

  \includegraphics[trim = 16mm 10mm 5mm 8mm, clip, keepaspectratio=true,
  width=0.73\textheight]{./figures/cosmicweb_FA_Tweb.pdf}
  \includegraphics[trim = 16mm 10mm 5mm 8mm, clip, keepaspectratio=true,
  width=0.73\textheight]{./figures/cosmicweb_FA_Vweb.pdf}

%.........................................................................
%FIGURE 2: Distributions of FA and density regarding the Lambda_1 eigenvalue
\begin{flushleft}
\begin{figure*}
\centering

@@

>>>>

%.........................................................................
%Table of sizes of each sample defined in Bolshoi
\begin{table}[h]
\begin{flushleft}
\begin{center}
  \begin{tabular}{l  r  r  r r} \hline\hline
	\textbf{Volume}					&				&\textbf{Scheme}& \\
	\textbf{Fraction}				&\textbf{T-web}	&\textbf{V-web}	&	\textbf{Density}  &  $\bf{\rho_{th}}$  \\ \hline
	Voids							&	$54.88\%$	&	$47.06\%$	&	$50.97\%$	&	$ -0.57$			\\ 
	Sheets							&	$33.21\%$	&	$39.54\%$	&	$36.38\%$ 	&	$0.60$				\\
	Filaments						&	$11.16\%$	&	$12.18\%$	&	$11.67\%$ 	&	$8.82$				\\
	Knots							&	$0.75\%$	&	$1.22\%$	&	$0.98\%$  	&	--		\\ \hline\hline
  \end{tabular}  
  \captionof{table}{\small Size of each sample defined in the Bolshoi 
  simulation and for each of the two schemes used to detect halos (FOF 
  and BDM).}

  \label{tab:Samples_Size}

\end{center}
\end{flushleft}
\end{table}
%.........................................................................

%.........................................................................
%FIGURE 1: Distributions of FA and density regarding the Lambda_1 eigenvalue
\begin{flushleft}
\begin{figure*}
\centering

@@

%.........................................................................
%FIGURE 1: Distributions of FA and density regarding the Lambda_1 eigenvalue
\begin{flushleft}
\begin{figure*}
\centering

  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/cosmicweb_volume_Tweb.pdf}
  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/cosmicweb_volume_Vweb.pdf}

%.........................................................................
%FIGURE 3: FA and vissual impression
\begin{flushleft}
\begin{figure*}
\centering

  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{./figures/cosmicweb_FA_Tweb.pdf}
  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{./figures/cosmicweb_FA_Vweb.pdf}
  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{./figures/cosmicweb_density.pdf}
